### 2017-01-03 paper/evaluation.tex
Reworked the purpose of RQ3
Updated evaluation motivation

\Mar{I think the high-level goal should be something along the lines
  of understanding prevalence of long test runs and main sources of
  cost in open-source Java projects.  Intuitively, the problem should
  come before the solution :).  Based on that, we study
  parallelization of testing frameworks.  More precisely, we
  investigage how prevalent test parallelization is, the potential for
  improving execution cost, issues of flakiness that hinders use of
  parallelization, and how to address those issues.}

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from \github{}. We are
interested in understanding the prevalence of long test runs, the main
sources of cost, and how do developers explore parallelism to improve
execution performance. More specifically, we pose the following
research questions:

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects.  The second research question
addresses our interest in understanding if developers are aware of
parallelization features from testing frameworks available
out-of-the-box through build systems (\eg, run JUnit test cases in
parallel using Maven Surefire) and what setting are more often used.
The third research question addresses the impact of parallelism on the
regression tests from our sample set. We are interested in compare the
execution performance with different parallel settings (see
Section~\ref{sec:modes}). The fourth research question addresses the
characteristics of regression tests from the previous experiment.
More specifically, we want to investigate if there is a relation
between the balance of test execution (\ie, how uniformly distributed
is the execution time across tests cases) and the usage of
computational resources (\ie, if tests are mostly CPU or IO intense)
that impacts the effectiveness of parallelization. Finally, the fifth
research question discusses the limitations and insights to overcome
the pitfalls of parallelization.

@@

We are interested to evaluate non-trivial test suites on popular
projects that are in activity. We used the \github{}'s search
API~\cite{githubsearch} to fetch Java projects according to the
following criteria: (1) the primary language must be Java\footnote{In
case of projects in multiple languages, the \github{} API considers the
predominant language as the primary language.}; (2) the project has at
least 100 stars; (3) latest update on (or after) January 1st, 2016;
(4) the \emph{readme} file contains the string \emph{mvn}.

>>>>

We are interested in understanding the prevalence of time-consuming
test suites and main sources of cost. We want to understand how the
execution cost is distributed on test cases withing a test suite and
how developers approach test execution. Based on that, we study
parallelization of testing frameworks.  More precisely, we investigate
how prevalent test parallelization is, the potential for improving
execution cost, issues of flakiness that hinders use of
parallelization, and how to address those issues.  More specifically,
we pose the following research questions:

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects.  The second research question
addresses our interest in understanding if developers are aware of
parallelization features from testing frameworks available
out-of-the-box through build systems (\eg, run JUnit test cases in
parallel using Maven Surefire) and what setting are more often used.
The third research question addresses the impact of parallelism on the
regression tests from our sample set. For subjects that use
parallelization settings, we are interested in compare the execution
performance when these settings are activated and deactivated (\ie,
sequential execution). The fourth research question addresses the
characteristics of regression tests from the previous experiment.
More specifically, we want to investigate if there is a relation
between the balance of test execution (\ie, how uniformly distributed
is the execution time across tests cases) and the usage of
computational resources (\ie, if tests are mostly CPU or IO intense)
that impacts the effectiveness of parallelization. Finally, the fifth
research question discusses the limitations and insights to overcome
the pitfalls of parallelization.

@@

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from \github{}.  We are
interested to evaluate non-trivial test suites on popular projects
that are in activity. We used the \github{}'s search
API~\cite{githubsearch} to fetch Java projects according to the
following criteria: (1) the primary language must be Java\footnote{In
case of projects in multiple languages, the \github{} API considers
the predominant language as the primary language.}; (2) the project
has at least 100 stars; (3) latest update on (or after) January 1st,
2016; (4) the \emph{readme} file contains the string \emph{mvn}.
